Safe Transferable Regions

### 2015-11-20 paper/introduction.tex
More small comments.

  \item We describe an implementation of \name frontend in OCaml,
  along with experimental results, and case studies where the region
  type system was able to identify unsafe memory accesses statically.

>>>>

  \item We describe an implementation of \name frontend in OCaml,
  along with experimental results, \dv{Experimental results of what?} and case studies where the region
  type system was able to identify unsafe memory accesses statically.
